Feature importance analysis

### 2020-05-06 analysis/feature-importance.Rmd
wflow_publish(knitr_in("analysis/feature-importance.Rmd"), view = FALSE,     verbose = TRUE)

    # HR: plot only rank 11:last
    geom_point(
      data = data_hr_merged[which(!(data_hr_merged$rank %in% c(1:10))), ],
      aes(color = "HR: Rank 11:122"),
      size = 1.8,
      shape = 1,
      na.rm = TRUE
    ) +
    # HR: plot only rank 1:10
    geom_point(
      data = data_hr_merged[which(data_hr_merged$rank %in% c(1:10)), ],
      aes(color = "HR: Rank 1:10"),
      shape = 20,
      size = 2.2,
      na.rm = TRUE
    ) +

@@

    # VI: rank 1:10
    geom_point(
      data = df_wavelengths_from_indices_imp[which((df_wavelengths_from_indices_imp$rank %in% c(1:10))), ],
      aes(x = wavelength, y = importance, group = class),
      size = 2.2, shape = 20
    ) +
    # VI: rank 1:10
    geom_line(
      data = df_wavelengths_from_indices_imp[which((df_wavelengths_from_indices_imp$rank %in% c(1:10))), ],
      aes(x = wavelength, y = importance, group = class, color = "VI: Rank 1:10"),
      size = 0.2, linetype = "dashed"
    ) +

    # VI: rank 11:89
    geom_point(
      data = df_wavelengths_from_indices_imp[which(!(df_wavelengths_from_indices_imp$rank %in% c(1:10))), ],
      aes(x = wavelength, y = importance, group = class),
      color = "grey",
      shape = 1, size = 2
    ) +
    # VI: rank 11:89
    geom_line(
      data = df_wavelengths_from_indices_imp[which(!(df_wavelengths_from_indices_imp$rank %in% c(1:10))), ],
      aes(x = wavelength, y = importance, group = class, color = "VI: Rank 11:89"),
      size = 0.2, linetype = "dashed"
    ) +

@@

ale_p1[[10]] = ale_p1[[10]] + scale_y_continuous(
  n.breaks = 5
)
ale_p1
```

>>>>

    # HR: plot only rank 11:last
    geom_point(
      data = data_hr_merged[which(!(data_hr_merged$rank %in% c(1:10))), ],
      aes(color = "HR: Rank 11:122"),
      size = 2.5,
      shape = 1,
      na.rm = TRUE
    ) +
    # HR: plot only rank 1:10
    geom_point(
      data = data_hr_merged[which(data_hr_merged$rank %in% c(1:10)), ],
      aes(color = "HR: Rank 1:10"),
      shape = 20,
      size = 3,
      na.rm = TRUE
    ) +

@@

    # VI: rank 1:10
    geom_point(
      data = df_wavelengths_from_indices_imp[which((df_wavelengths_from_indices_imp$rank %in% c(1:10))), ],
      aes(x = wavelength, y = importance, group = class),
      size = 3, shape = 20
    ) +
    # VI: rank 1:10
    geom_line(
      data = df_wavelengths_from_indices_imp[which((df_wavelengths_from_indices_imp$rank %in% c(1:10))), ],
      aes(x = wavelength, y = importance, group = class, color = "VI: Rank 1:10"),
      size = 0.2, linetype = "dashed"
    ) +

    # VI: rank 11:89
    geom_point(
      data = df_wavelengths_from_indices_imp[which(!(df_wavelengths_from_indices_imp$rank %in% c(1:10))), ],
      aes(x = wavelength, y = importance, group = class),
      color = "grey",
      shape = 1, size = 2.5
    ) +
    # VI: rank 11:89
    geom_line(
      data = df_wavelengths_from_indices_imp[which(!(df_wavelengths_from_indices_imp$rank %in% c(1:10))), ],
      aes(x = wavelength, y = importance, group = class, color = "VI: Rank 11:89"),
      size = 0.2, linetype = "dashed"
    ) +

@@

ale_p1[[10]] = ale_p1[[10]] + scale_y_continuous(
  n.breaks = 4
)
ale_p1
```
